Log or not

### 2021-10-25 analysis/Analysis.Rmd
update plots

```{r}
results

@@

  res |> 
    ggplot(aes(x = error, y = multplicative_score, 
               colour = `True parameters`, group = `True parameters`)) + 
    geom_line() + 
    scale_color_brewer(palette = "Set1", name = "True parameters: ") + 
    # scale_y_continuous(limits = c(1, NA), expand = c(0, NA)) + 
    expand_limits(y = c(1, NA)) + 
    facet_wrap( ~ error_title + scale, scale = "free", nrow = 2) + 
    theme_minimal() + 
    theme(legend.position = "bottom") +
    labs(y = "Multiplicative change in Interval Score", 
         x = "Error") + 
    geom_rect(data = subset(res, error_var == "sigma"), 
              fill = NA, colour = "grey80", xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf) + 
    geom_rect(data = subset(res, error_var == "mu"), 
              fill = NA, colour = "grey70", xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf) 
}
```

@@

```{r}
p1 <- plot_multiple(res, equal_means = TRUE, equal_vars = TRUE) 
ggsave(p1, filename = here("output", "effect_equal_mean_equal_var.png"))

p1 + 
  ggtitle("Effect of scoring on a log scale")
```

@@

```{r}
p2 <- plot_multiple(res, equal_means = FALSE, equal_vars = TRUE) 
ggsave(p2, filename = here("output", "effect_unequal_mean_equal_var.png"))

p2 + 
  ggtitle("Effect of scoring on a log scale for two variables with unequal means")
```

@@

```{r}
p3 <- plot_multiple(res, equal_means = TRUE, equal_vars = FALSE) 
ggsave(p3, filename = here("output", "effect_equal_mean_unequal_var.png"))

p3 + 
  ggtitle("Effect of scoring on a log scale for two variables with unequal variances")
```

```{r}
p4 <- plot_multiple(res, equal_means = FALSE, equal_vars = FALSE) 
ggsave(p4, filename = here("output", "effect_unequal_mean_unequal_var.png"))

title <- "Effect of scoring on a log scale for two variables with unequal means and unequal variances"
p4 + 
  ggtitle(wrap_title(title, width = 80))
```

>>>>

```{r eval=rerun_simulation}
results

@@

  res |> 
    ggplot(aes(x = error, y = multplicative_score, 
               colour = `True parameters`, group = `True parameters`)) + 
    geom_line() + 
    scale_color_brewer(palette = "Set1", name = "True parameters: ") + 
    # scale_y_continuous(limits = c(1, NA), expand = c(0, NA)) + 
    expand_limits(y = c(1, NA)) + 
    facet_wrap( ~ error_title + scale, scale = "free", nrow = 2) + 
    theme_minimal() + 
    theme(legend.position = "bottom") +
    labs(y = "Multiplicative change in Interval Score", 
         x = "Error") + 
    geom_rect(data = subset(res, error_var == "sigma"), 
              fill = NA, colour = "grey80", xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf) + 
    geom_rect(data = subset(res, error_var == "mu"), 
              fill = NA, colour = "grey70", xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf) 
}

p1 <- plot_multiple(res, equal_means = TRUE, equal_vars = TRUE) 
ggsave(p1, filename = here("output", "effect_equal_mean_equal_var.png"))

p2 <- plot_multiple(res, equal_means = FALSE, equal_vars = TRUE) 
ggsave(p2, filename = here("output", "effect_unequal_mean_equal_var.png"))

p3 <- plot_multiple(res, equal_means = TRUE, equal_vars = FALSE) 
ggsave(p3, filename = here("output", "effect_equal_mean_unequal_var.png"))

p4 <- plot_multiple(res, equal_means = FALSE, equal_vars = FALSE) 
ggsave(p4, filename = here("output", "effect_unequal_mean_unequal_var.png"))

@@

Effect of scoring on a log scale

```{r}
knitr::include_graphics(here("output", "effect_equal_mean_equal_var.png"))
```

@@

Effect of scoring on a log scale for two variables with unequal means

```{r}
knitr::include_graphics(here("output", "effect_unequal_mean_equal_var.png"))
```

@@

Effect of scoring on a log scale for two variables with unequal variances

```{r}
knitr::include_graphics( here("output", "effect_equal_mean_unequal_var.png"))
```

Effect of scoring on a log scale for two variables with unequal means and unequal variances

```{r}
knitr::include_graphics(here("output", "effect_unequal_mean_unequal_var.png"))
```
